PCA

### 2019-11-23 analysis/11_pcalda.Rmd
new pca

```{r pca}
a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue,
                         alpha = colData$sex)) +
  geom_point(size = 2)  + theme_minimal(base_size = 6)  +
  mytheme() +
  theme(legend.title = element_blank(), 
        axis.text = element_blank()) +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(x = "PC1: 35.9% of variance", y = "PC2: 32.5% of variance")

@@

>>>>

```{r pca}
a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue)) +
  geom_point(size = 3)  + theme_minimal(base_size = 6)  +
  mytheme() +
  theme(legend.title = element_blank(), 
        axis.text = element_blank()) +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(x = "PC1: 35.9% of variance", y = "PC2: 32.5% of variance")

@@

```{r pca2}
plot_grid(a + theme(legend.position = "none"),
          b + theme(axis.text = element_blank()), 
          nrow = 1, rel_widths = c(0.7,0.3))
```
